Identification and performance of stock-recruitment functions in state

### 2024-02-08 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
presentation done?
presentation update

## Some Example OM Simulated Data (100 data sets for each OM)
- still need to make this

@@

# Sims
## Simulated Data Examples - Type 1
- plots

## Simulated Data Examples - Type 2
- plots

## Simulated Data Examples - Type 3
- plots

>>>>

@@

# Sims
## Simulated Data Examples - Type 1
```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'recruit_ecov.pdf') )
```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='50%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'stock_recruit_no_ecov.pdf') )
```

## Simulated Data Examples - Recruitment Timeseries
```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='90%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'Rec_sims.png') )
```

<!-- ```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='40%', fig.align='center'} -->
<!--  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'om_57.59.61.63.121.123.125.127.185.187.189.191.249.251.253.255._Recr.plot.png') ) -->
<!-- ``` -->

## Simulated Data Examples - SSB Timeseries
```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='90%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'SSB_sims.png') )
```

<!-- ```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='40%', fig.align='center'} -->
<!--  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'om_57.59.61.63.121.123.125.127.185.187.189.191.249.251.253.255._SSB.png') ) -->
<!-- ``` -->
